---
title: "nat_catcher_fun"
author: "Olga Chyzh"
date: "January 18, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Load the libraries:

```{r}

rm(list = ls())
library(tidyverse)
library(data.table)
```

The function that calculates the number of white nat followers:

```{r}
nat_catcher<-function(myrep, path){
  mypath<-paste(path,myrep,sep="")
  mydata<-fread(mypath, header=TRUE)

#Now want to replace certain words in description (e.g., "White House" or "teeth whitening) with spaces:
desc_clean<-mydata$description


#table(grepl("White House",desc_clean, ignore.case = TRUE))
clist <- c("White House", "WhiteHouse", "teeth whitening", "Go White", "Red White and Blue","Red, White, and Blue",
           "Red, White and Blue","Red,White,&Blue","Red,White and Blue","white silence is violence","RedWhite&Blue",
           "black and white","white-label","whiteboard","whitetails","whitefield","white sox","whitesox")
for (i in clist) {
  desc_clean<-gsub(i, "",desc_clean,ignore.case = TRUE)

}



wd<-as.numeric(grepl("White",desc_clean, ignore.case = TRUE)==TRUE | 
                      grepl("altright",desc_clean, ignore.case = TRUE)==TRUE |
                      grepl("alt-right",desc_clean, ignore.case = TRUE)==TRUE |
                      grepl("alt right",desc_clean, ignore.case = TRUE)==TRUE |
                      grepl("Aryan",desc_clean, ignore.case = FALSE)==TRUE |
                      grepl("ethno-nationalist",desc_clean, ignore.case = FALSE)==TRUE |
                      grepl("identitarian",desc_clean, ignore.case = FALSE)==TRUE |
                      grepl("14words",desc_clean, ignore.case = FALSE)==TRUE |
                      grepl("\u26a1?\u26a1 ",desc_clean, ignore.case = FALSE)==TRUE 
                       )
tot<-nrow(mydata)

return(cbind(myrep,sum(wd),tot))

}



```

Apply the nat_catcher:

```{r}
#Get the list of filenames that store info on followers:
myreps<-list.files("./house_foll1/")
rep_scores<-lapply(myreps,nat_catcher, path="./house_foll1/")
rep_scores<-as.data.frame(matrix(unlist(rep_scores),518,3, byrow=TRUE))
names(rep_scores)<-c("handle_mod","natfol","totfol")

#Get partial handle var for merging with USreps 
rep_scores$handle_mod<-gsub(".csv", "", rep_scores$handle_mod)
rep_scores$handle_part<-gsub('[[:digit:]]+', '', rep_scores$handle_mod)

rep_scores$natfol<-as.numeric(as.character(rep_scores$natfol))
rep_scores$totfol<-as.numeric(as.character(rep_scores$totfol))
head(rep_scores)

#Get the twitter handles:

rep_scores1<-rep_scores %>% group_by(handle_part) %>%
    mutate(handle = dplyr::first(handle_mod), natfol=sum(natfol), totfol=sum(totfol))
rep_scores1<-unique(rep_scores1[,2:5])

#Get a list of accounts with more than 90000 followers:
pop_list<-function(x, path){
  oname<-paste(path,x,sep="")
  myfile<-read.csv(oname, header=TRUE)
  if (length(myfile$user_id)>90000) {
    x<-gsub(".csv", "", x)
    rep_popular<-c(rep_popular,x)
  } 
}

myfiles<-list.files("./house_out/")
rep_popular<-NULL

rep_popular<-lapply(myfiles, pop_list, path="./house_out/")
rep_popular<-unique(unlist(rep_popular))

rep_scores1$handle<-as.character(rep_scores1$handle)
rep_scores1$handle[rep_scores1$handle_part %in% rep_popular==TRUE]<- substr(rep_scores1$handle[rep_scores1$handle_part %in% rep_popular==TRUE],1, nchar(rep_scores1$handle[rep_scores1$handle_part %in% rep_popular==TRUE]) -1)


```

Add the additional accounts that we missed originally:
```{r}
#Get the list of filenames that store info on followers:
myreps<-list.files("./house_foll_add/")
rep_scores<-lapply(myreps,nat_catcher, path="./house_foll_add/")


rep_scores<-as.data.frame(matrix(unlist(rep_scores),41,3, byrow=TRUE))
names(rep_scores)<-c("handle_mod","natfol","totfol")

#Get partial handle var for merging with USreps 
rep_scores$handle_mod<-gsub(".csv", "", rep_scores$handle_mod)
rep_scores$handle_part<-gsub('[[:digit:]]+', '', rep_scores$handle_mod)

rep_scores$natfol<-as.numeric(as.character(rep_scores$natfol))
rep_scores$totfol<-as.numeric(as.character(rep_scores$totfol))
head(rep_scores)

#Get the twitter handles:

rep_scores2<-rep_scores %>% group_by(handle_part) %>%
    mutate(handle = dplyr::first(handle_mod), natfol=sum(natfol), totfol=sum(totfol))
rep_scores2<-unique(rep_scores2[,2:5])

#Get a list of accounts with more than 90000 followers to correct some handles:
myfiles<-list.files("./house_out_add/")
rep_popular<-NULL
rep_popular<-lapply(myfiles, pop_list, path="./house_out_add/")
rep_popular<-unique(unlist(rep_popular))

rep_scores2$handle<-as.character(rep_scores2$handle)
rep_scores2$handle[rep_scores2$handle_part %in% rep_popular==TRUE]<- substr(rep_scores2$handle[rep_scores2$handle_part %in% rep_popular==TRUE],1, nchar(rep_scores1$handle[rep_scores2$handle_part %in% rep_popular==TRUE]) -1)

```




Merge the results with a data on US Reps: 
```{r}
rep_scores<-rbind.data.frame(rep_scores1,rep_scores2)
rep_scores<-rep_scores %>% ungroup %>% mutate(prop_nats=natfol/totfol)
#Open the file that contains cleaned up names and nat scores:
mydata<-read.csv("USreps.csv", header=TRUE)
head(mydata)



mydata1<-left_join(mydata, rep_scores, by="handle_part")
write.csv(mydata1, "Repswscores.csv", row.names = FALSE)
```


#Code name based on the twitter handle:
scores[,1]<-gsub(".csv", "", scores[,1])
scores[,1]<-gsub('[[:digit:]]+', '', scores[,1])
scores$score<-as.numeric(as.character(scores[,2]))
scores$tot_fol<-as.numeric(as.character(scores[,3]))

#Get correct natscores for popular reps whose followers were broken up in multiple files:
scores<-aggregate(cbind(score,tot_fol)~V1,data=scores,FUN=sum)


scores$name<-gsub('([[:upper:]])', ' \\1', scores[,1])
scores$name<-gsub("Mc ", "Mc", scores$name)
scores$name<-sub("rep", "", scores$name, ignore.case=TRUE)
scores$name<-sub("^\\s+", "", scores$name)
scores$fname<-word(scores$name, 1)
scores$lname<-word(scores$name, 2)

write.csv(scores,"scores.csv", row.names=FALSE)


#Get total number of followers for each account:
#for (i in seq(1:length(houseaccounts))) {



get_tot_followers<-function(accountname, acctpath){
  oname<-paste(acctpath,accountname, sep="")
  rep<-read.csv(oname, header=TRUE)
  tot<-length(rep$user_id)
  name<-gsub(".csv", "", accountname)
  return(cbind(name,tot))
}

filenames<-list.files(path="house_out/", pattern="*.csv")
#get_tot_followers(filenames[1],acctpath="house_out/")
mytots<-lapply(filenames,get_tot_followers,acctpath="house_out/")

totfol<-unlist(mytots)
totfol<-matrix(totfol,(length(totfol)/2),2, byrow=TRUE)
head(totfol)
dim(totfol)

#Get total natscore for popular reps whose followers were broken up in multiple files:
totfol<-as.data.frame(totfol)
names(totfol)<-c("handle","tot_fol")
totfol$tot_fol<-as.numeric(as.character(totfol$tot_fol))
totfol$handle<-gsub('[[:digit:]]+', '', totfol$handle)
totfol<-aggregate(tot_fol~handle,data=totfol,FUN=max)
dim(totfol)


#This is to get the additional reps that we missed the first time:
filenames1<-list.files(path="house_out_add/", pattern="*.csv") #Reps missed the first time around


scores<-read.csv("scores.csv", header=TRUE)
scores<-subset(scores, select=c("V1","score","tot_fol"))

#Open the file that contains cleaned up names and nat scores:
mydata<-read.csv("scores_wnames.csv", header=TRUE)
mydata$score<-NULL
head(mydata)
dim(mydata)

mydata1<-merge(mydata, scores, by.x="V1", by.y="V1", all.x=TRUE)
write.csv(mydata1, "scores_wnames_and_tots.csv", row.names = FALSE)

